Tables in the project

### 2018-08-09 paper/Chapters/Chapter3.tex
regression table added

		\multicolumn{7}{l}{\textit{Note: }}\\
		\multicolumn{7}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}\\
		\multicolumn{7}{l}{Variables are weighted by nurse visiting weights.}\\
		\multicolumn{7}{l}{\textsuperscript{*} Significant sex-specific differences by hypertension status assessed using an \textit{F} test for continuous variables or design-adjusted Pearson $\chi^2$ test.}\\
		\multicolumn{7}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership.}\\
		\multicolumn{7}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}\\
		\multicolumn{7}{l}{\textsuperscript{\S}  DM was defined by A1C $>$ 6.5\%.}

@@

			\multicolumn{9}{l}{\textit{Note: }}\\
			\multicolumn{9}{l}{\textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}\\
			\multicolumn{9}{l}{Variables are weighted by nurse visiting weights.}\\
			\multicolumn{9}{l}{\textsuperscript{*} Significant sex-specific differences by BMI categories assessed using an \textit{F} test (with Bonferroni correction to account for multiple testing across $>$ 2 groups)} \\ 
			\multicolumn{9}{l}{for continuous variables or design-adjusted Pearson $\chi^2$ test for categorical variables}\\
			\multicolumn{9}{l}{\textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership.}\\
			\multicolumn{9}{l}{\textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}\\

@@

>>>>

		\multicolumn{7}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{7}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}}\\
		\multicolumn{7}{l}{{\scriptsize Variables are weighted by nurse visiting weights.}}\\
		\multicolumn{7}{l}{{\scriptsize \textsuperscript{*} Significant sex-specific differences by hypertension status assessed using an \textit{F} test for continuous variables or design-adjusted Pearson $\chi^2$ test.}}\\
		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership.}}\\
		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}}\\
		\multicolumn{7}{l}{{\scriptsize \textsuperscript{\S}  DM was defined by A1C $>$ 6.5\%.}}

@@

			\multicolumn{9}{l}{{\scriptsize \textit{Note: }}}\\
			\multicolumn{9}{l}{{\scriptsize \textbf{Abbreviations}: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme; BMI body mass index; WC, waist circumference.}}\\
			\multicolumn{9}{l}{{\scriptsize Variables are weighted by nurse visiting weights.}}\\
			\multicolumn{9}{l}{{\scriptsize \textsuperscript{*} Significant sex-specific differences by BMI categories assessed using an \textit{F} test (with Bonferroni correction to account for multiple testing across $>$ 2 groups)}} \\ 
			\multicolumn{9}{l}{{\scriptsize for continuous variables or design-adjusted Pearson $\chi^2$ test for categorical variables}}\\
			\multicolumn{9}{l}{{\scriptsize \textsuperscript{\ddag} Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership.}}\\
			\multicolumn{9}{l}{{\scriptsize \textsuperscript{\dag} Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities.}}\\

@@

		\caption{\label{tab:survgression}Associations of carbohydrate eating patterns with hypertension, BMI, WC, and DM in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).}
		\begin{tabular}[t]{lccccccccccc}
			\multicolumn{1}{c}{ } & \multicolumn{5}{c}{Men (n = 2537)} & \multicolumn{6}{c}{Women (n = 3618)} \\
			\cmidrule(l{2pt}r{2pt}){2-6} \cmidrule(l{2pt}r{2pt}){7-12}
			Models & Low & Moderate & P value\textsuperscript{*} & High & P value & Models & Low & Moderate & P value & High & P value\\
			\addlinespace[0.3em]
			\multicolumn{12}{l}{\textbf{Hypertension}}\\
			\hspace{1em}Crude model & 1 & 0.48 (0.33, 0.70) & < 0.001 & 0.82 (0.59, 1.13) & 0.217 & Crude model & 1 & 0.52 (0.36, 0.75) & < 0.001 & 0.96 (0.72, 1.28) & 0.773\\
			\hspace{1em}Model 1\textsuperscript{\dag} & 1 & 0.68 (0.43, 1.07) & 0.093 & 0.80 (0.56, 1.15) & 0.227 & Model 1\textsuperscript{\ddag} & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.89 (0.61, 1.30) & 0.552\\
			\hspace{1em}Model 2 & 1 & 0.64 (0.41, 1.01) & 0.054 & 0.75 (0.53, 1.08) & 0.124 & Model 2 & 1 & 0.78 (0.45, 1.36) & 0.384 & 0.88 (0.62, 1.26) & 0.483\\
			\addlinespace[0.3em]
			\multicolumn{12}{l}{\textbf{Hypertension in non-diabetics}}\\
			\hspace{1em}Crude model & 1 & 0.49 (0.33, 0.73) & < 0.001 & 0.82 (0.59, 1.14) & 0.241 & Crude model & 1 & 0.51 (0.35, 0.74) & < 0.001 & 0.98 (0.73, 1.31) & 0.875\\
			\hspace{1em}Model 1 & 1 & 0.69 (0.43, 1.09) & 0.11 & 0.78 (0.54, 1.14) & 0.197 & Model 1 & 1 & 0.79 (0.44, 1.42) & 0.435 & 0.89 (0.61, 1.29) & 0.534\\
			\hspace{1em}Model 2 & 1 & 0.65 (0.41, 1.03) & 0.066 & 0.73 (0.51, 1.06) & 0.096 & Model 2 & 1 & 0.79 (0.45, 1.39) & 0.415 & 0.87 (0.61, 1.25) & 0.452\\
			\addlinespace[0.3em]
			\multicolumn{12}{l}{\textbf{BMI}}\\
			\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426 & Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
			\hspace{1em}Model 1\textsuperscript{\S} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0,43 (-1.13, 0.26) & 0.22 & Live with partner\textsuperscript{\P} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
			\hspace{1em} &  &  &  &  &  & Live alone & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
			\addlinespace[0.3em]
			\multicolumn{12}{l}{\textbf{BMI in non-diabetics}}\\
			\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557 & Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.04\\
			\hspace{1em}Model 1 & -- & -0.10 (-0.97, 0.77) & 0.82 & -0.39 (-1.10, 0.31) & 0.269 & Live with partner & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
			\hspace{1em} &  &  &  &  &  & Live alone & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
			\addlinespace[0.3em]
			\multicolumn{12}{l}{\textbf{WC}}\\
			\hspace{1em}Crude model & -- & -3.00 (-5.49, -0.52) & 0.018 & -0.90 (-2.84, 1.04) & 0.364 & Crude model & -- & -1.28 (-3.26, 0.70) & 0.206 & -2.81 (-4.50, -1.12) & 0.001\\
			\hspace{1em}Model 1\textsuperscript{**} & -- & 1.06 (-1.50, 3.64) & 0.415 & -1.55 (-3.42, 0.31) & 0.103 & Live with partner\textsuperscript{\dag\dag} & -- & 0.28 (-2.85, 3.41) & 0.861 & -4.71 (-7.00, -2.43) & < 0.001\\
			\hspace{1em} &  &  &  &  &  & Live alone & -- & 3.17 (0.05, 6.30) & 0.047 & 0.73 (-1.84, 3.30) & 0.577\\
			\addlinespace[0.3em]
			\multicolumn{12}{l}{\textbf{WC in non-diabetics}}\\
			\hspace{1em}Crude model & -- & -2.51 (-5.00, -0.21) & 0.048 & -0.51 (-2.47, 1.44) & 0.606 & Crude model & -- & -0.91 (-2.88, 1.07) & 0.368 & -2.41 (-4.06, -0.76) & 0.004\\
			\hspace{1em}Model 1 & -- & 1.42 (-1.17, 4.01) & 0.283 & -1.29 (-3.18, 0.60) & 0.181 & Live with partner & -- & 1.11 (-2.02, 4.23) & 0.487 & -3.74 (-5.97, -1.51) & 0.001\\
			\hspace{1em} &  &  &  &  &  & Live alone & -- & 3.08 (-0.09, 6.25) & 0.057 & 0.16 (-2.36, 2.69) & 0.899\\
			\addlinespace[0.3em]
			\multicolumn{12}{l}{\textbf{DM}}\\
			\hspace{1em}Crude model & 1 & 0.39 (0.18, 0.83) & 0.016 & 0.78 (0.43, 1.42) & 0.416 & Crude model & 1 & 0.65 (0.28, 1.47) & 0.296 & 0.38 (0.18, 0.81) & 0.013\\
			\hspace{1em}Model 1\textsuperscript{\ddag\ddag} & 1 & 0.27 (0.10, 0.73) & 0.012 & 0.78 (0.36, 1.68) & 0.529 & Model 1\textsuperscript{\S\S} & 1 & 1.05 (0.33, 3.35) & 0.928 & 0.52 (0.17, 1.59) & 0.255\\
			\hspace{1em}Model 2 & 1 & 0.27 (0.10, 0.76) & 0.013 & 0.76 (0.35, 1.65) & 0.493 & Model 2 & 1 & 0.79 (0.25, 2.46) & 0.686 & 0.48 (0.18, 1.32) & 0.155\\
			\multicolumn{12}{l}{{\scriptsize \textit{Note: }}}\\
			\multicolumn{12}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
			\multicolumn{12}{l}{{\scriptsize DM was defined by A1C > 6.5\%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.}}\\
			\multicolumn{12}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from either linear regression models or logistic regression models.}}\\
			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or not, BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);}}\\
			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);}}\\
			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\S} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;}}\\
			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\P} Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;}}\\
			\multicolumn{12}{l}{{\scriptsize \textsuperscript{**} Adjusted for age, live with partner or not, average household income, education level, hypertension, smoking, total energy intake, alcohol consumption;}}\\
			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\dag\dag} Adjusted for age, live with partner or not, education level, hypertension, total energy intake, alcoho consumpiont;}}\\
			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\ddag\ddag} Adjusted for age, average household income, education level, BMI, hypertension, smoking status, total energy intake, ethnicity (white or non-white), alcohol consumption,}}\\ 
			\multicolumn{12}{l}{{\scriptsize TC (mmol/l), LDL (mmol/l), HDL (mmol/l), TG (mmol/l);}}\\
			\multicolumn{12}{l}{{\scriptsize \textsuperscript{\S\S} Adjusted for age, education level, BMI, hypertension, smoking status, total energy intake, alcohol consumption, TC, LDL, HDL, TG.}}\\

### 2018-08-09 paper/Tables/2by2Table1.Rmd
regression table added

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
  add_indent(c(6:9, 11,12, 14,15, 17:19, 22:24)) %>% 
   add_header_above(c(" ", "Men (n = 2537)" = 4, "Women (n = 3618)" = 4)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",  
                       " BMI body mass index; WC, waist circumference.", 
                       "Variables are weighted by nurse visiting weights.")) %>% 
  add_footnote(c("Significant sex-specific differences by BMI categories assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups) for continuous variables or design-adjusted Pearson chi-square test",
                 # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
                 # # "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
                 # "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",
                 # "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 # "DM was defined by A1C > 6.5%.",
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey."
                 ), 
               notation = "symbol")
```

@@

@@

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by hypertension status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
  add_indent(c(6:9, 11,12, 14,15, 17:19, 22:24)) %>% 
   add_header_above(c(" ", "Men (n = 2537)" = 4, "Women (n = 3618)" = 4)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",  
                       " BMI body mass index; WC, waist circumference.", 
                       "Variables are weighted by nurse visiting weights.")) %>% 
  add_footnote(c("Significant sex-specific differences by BMI categories assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups) for continuous variables or design-adjusted Pearson chi-square test",
                 # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
                 # # "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
                 # "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",
                 # "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 # "DM was defined by A1C > 6.5%.",
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey."
                 ), 
               notation = "symbol")
```

>>>>

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by BMI status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
  add_indent(c(6:9, 11,12, 14,15, 17:19, 22:24)) %>% 
   add_header_above(c(" ", "Men (n = 2537)" = 4, "Women (n = 3618)" = 4)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",  
                       " BMI body mass index; WC, waist circumference.", 
                       "Variables are weighted by nurse visiting weights.")) %>% 
  add_footnote(c("Significant sex-specific differences by BMI categories assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups) for continuous variables or design-adjusted Pearson chi-square test",
                 # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
                 # # "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
                 # "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",
                 # "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 # "DM was defined by A1C > 6.5%.",
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey."
                 ), 
               notation = "symbol")
```

@@

```{r tab1DM, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/DMtab1.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c(" ", "Non-diabetes", "Diabetes", "P value[note]", 
               "Non-diabetes", "Diabetes", "P value")

@@

dt[18, 1] <- c("Physical\nactivity (hours/day) [note]")
# dt[20, 1] <- c("DM [note]")
# dt[20, 1] <- c("Paid employment[note] (%)")
# dt[23, 1] <- c("Live with partner[note] (%)")

kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Weighted means, percentages, and 95 CIs of the characteristics by diabetic status in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>% 
  add_indent(c(6:7, 9, 10, 12, 13, 15:17, 22:24)) %>% 
   add_header_above(c(" ", "Men (n = 2537)" = 3, "Women (n = 3618)" = 3)) %>% 
  footnote(general = c("Abbreviations: CI, confidence intervals; NDNS RP, national dietary and nutrition survey rolling programme;",  
                       " BMI body mass index; WC, waist circumference.", 
                       "Variables are weighted by nurse visiting weights.")) %>% 
  add_footnote(c("Significant sex-specific differences by diabetic status assessed using an F test (with Bonferroni correction to account for multiple testing across $>$ 2 groups) for continuous variables or design-adjusted Pearson chi-square test",
                 # "Paid employment was defined as being in paid employment during the last 4 weeks prior to the survey." , 
                 # # "Live with partner was defined as either living with a married husband/wife or a legally recognised civil partnership."
                 # "Hypertension was defined as either systolic blood pressure >= 140 mmHg or diastolic blood pressure >= 90 mmHg, or under treatment for hypertension.",
                 # "Carbohydrate percent indicates the percentage of energy from carbohydrate in total energy intake",
                 # "DM was defined by A1C > 6.5%.",
                 "Physical activity was calculated as mean time spent at moderate or vigorous physical activity including both work-related and recreational activities during the survey."
                 ), 
               notation = "symbol")
```

## Table 2 regressions in survey

```{r survgression, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dt <- read.csv("/home/wangcc-me/Documents/LSHTMproject/Tablecsv/SurveyReg.csv", header = T, row.names = NULL, colClasses = "character")
names(dt) <- c("Models", "Low", "Moderate", "P value[note]", "High", "P value", "Models", "Low", "Moderate", "P value", "High", "P value")
dt[2, 1] <- c("Model 1[note]")
dt[2, 7] <- c("Model 1[note]")
dt[8, 1] <- c("Model 1[note]")
dt[8, 7] <- c("Live with partner[note]")
dt[14, 1] <- c("Model 1[note]")
dt[14, 7] <- c("Live with partner[note]")
dt[20, 1] <- c("Model 1[note]")
dt[20, 7] <- c("Model 1[note]")
kable(dt,  align = "l", row.names = FALSE,
              format = "latex", caption = "Associations of carbohydrate eating patterns with hypertension, BMI, WC, and DM in the UK adults (NDNS RP 2008/09-2015/16, sample size = 6155).", booktabs = T,linesep = "") %>%
 kable_styling(latex_options = c("striped"), font_size = 9) %>%
  group_rows("Hypertension", 1, 3) %>%
  group_rows("Hypertension in non-diabetics", 4, 6) %>% 
  group_rows("BMI", 7, 9) %>%
  group_rows("BMI in non-diabetics", 10, 12) %>%
    group_rows("WC", 13, 15) %>%
  group_rows("WC in non-diabetics", 16, 18) %>%
  group_rows("DM", 19, 21) %>%
   add_header_above(c(" ", "Men (n = 2537)" = 5, "Women (n = 3618)" = 6)) %>% 
  footnote(general = c("Abbreviations: BMI body mass index; WC, waist circumference; NDNS RP, national dietary and nutrition survey rolling programme.",
                       "DM was defined by A1C > 6.5%. BMI was replaced with WC in Model 2s, other covariates remained the same with the corresponding Model 1s.")) %>% 
  add_footnote(c("P values were obtained from wald tests from either linear regression models or logistic regression models.",
                "Adjusted for age (continuous), live with partner or not (binary), education level (higher or equal to degree level or not, BMI, smoking status (current, ex-smoker, never), total energy intake (kJ);", 
                "Adjusted for age, live with partner or not, average household income (continuous), education level, BMI, smoking status, total energy intake (kJ), alcohol consumption (g/day);", 
                "Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total energy intake, alcohol consumption;", 
                "Adjusted for age, average household income, education level, smoking status, total energy intake, alcohol consumption;", 
                "Adjusted for age, live with partner or not, average household income, education level, hypertension, smoking, total energy intake, alcohol consumption;", 
                "Adjusted for age, live with partner or not, education level, hypertension, total energy intake, alcoho consumpiont;", 
                "Adjusted for age, average household income, education level, BMI, hypertension, smoking status, total energy intake, ethnicity (white or non-white), alcohol consumption, TC (mmol/l), LDL (mmol/l), HDL (mmol/l), TG (mmol/l);", 
                "Adjusted for age, education level, BMI, hypertension, smoking status, total energy intake, alcohol consumption, TC, LDL, HDL, TG."), 
               notation = "symbol")
```
